Simulating Financial Markets using MASON Framework\thanks{Prepared for the 2nd World Congress on Social Simulation, GMU, Fairfax, 14--17 July, 2008.}

### 2008-05-06 documents/WCSS2008Paper/paper.tex
Added sequence diagram to the presentation and paper
Renamed plots from Farmer with a 'Farmer-' prefix. Replaced acf and return histogram plots with representative examples. Updated paper.tex to point to these files.

\begin{figure}[htb]
\centering
\includegraphics[width=1.0\textwidth]{../graphics/masterClassDiagram.jpg}
\caption{High-level UML class diagram of the main components and relations in the FinancialMarketModel, including the main attributes of Players and OrderBooks. Agent classes (light blue) inherit from the MASON \texttt{Steppable} interface while the master class is implementation of MASON's \texttt{SimState}.}
\label{fig:general_uml}
\end{figure}

>>>>

\begin{figure}[htb]
\centering
\includegraphics[width=1.0\textwidth]{../graphics/masterClassDiagram.pdf}
\caption{High-level UML class diagram of the main components and relations in the FinancialMarketModel, including the main attributes of Players and OrderBooks. Agent classes (light blue) inherit from the MASON \texttt{Steppable} interface while the master class is implementation of MASON's \texttt{SimState}.}
\label{fig:general_uml}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=1.0\textwidth]{../graphics/masterSequenceDiagram.pdf}
\caption{High-level UML sequence diagram of the interactions between main object of the FinancialMarketModel.}
\label{fig:general_uml}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
   \mbox{
      \subfigure[Ask and bid prices.]{\scalebox{0.5}{\quad \quad \includegraphics[width=0.9\textwidth,height=0.8\textwidth]{../graphics/Farmer-pricesPlot.pdf}}} \quad
      \subfigure[Raw and absolute returns.]{\scalebox{0.5}{\includegraphics[width=1.00\textwidth]{../graphics/Farmer-returnPlot.pdf}}}
      }
    \mbox{
      \subfigure[Orderbook shape.]{\scalebox{0.5}{\includegraphics[width=1.00\textwidth]{../graphics/Farmer-orderbooks.pdf}}} \quad
      \subfigure[Trade volumes.]{\scalebox{0.5}{\includegraphics[width=1.00\textwidth]{../graphics/Farmer-volumesPlot.pdf}}}
      }
    \mbox{
      \subfigure[Returns histogram.]{\scalebox{0.5}{\includegraphics[width=1.00\textwidth]{../graphics/Farmer-returnsHistogram.pdf}}} \quad
      \subfigure[Autocorrelation of returns.]{\scalebox{0.5}{\includegraphics[width=1.00\textwidth]{../graphics/Farmer-acfReturns.pdf}}}
      }
    \caption{Examples of outputs and statistics from a single run of the FinancialModel simulation for default Farmer's parametrization.}
    \label{fig:sampleDynamics}
  \end{center}
\end{figure}
